Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-05-31 EMNLP-demo-paper/result.tex
minor fix

\subsection{Natural Language Inference}
\label{sec:NLIexample}
The NLI task predicts the relationship between a premise sentence (\textbf{P}) and a hypothesis sentence (\textbf{H}).
The attention matrix captures the alignment of words between these two sentences.
Here we give an example of how a wrong prediction can be correct by editing the attention value.

@@

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea". However, these two \emph{green}`s decorate different nouns, which potentially lead to the wrong prediction. The grammar structure is visually presented by dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

>>>>

\subsection{Natural Language Inference}
\label{sec:NLIexample}
The NLI task predicts the relationship between a premise sentence (P) and a hypothesis sentence (H).
The attention matrix captures the alignment of words between these two sentences.
Here we give an example of how a wrong prediction can be correct by editing the attention value.

@@

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (P:``A woman in a green jacket is drinking tea.'' H:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea". However, these two \emph{green}`s decorate different nouns, which potentially lead to the wrong prediction. The grammar structure is visually presented by dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).
